Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
update section2

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.  we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.

>>>>

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
